---
title: "Quarto Basics (Answers)"
author: "Nicholas Vietto"
format: html
editor: source
toc: true
toc-location: left
theme: sketchy
self-contained: true

---

Some basic things to know about creating an HTML Quarto doc! 


1.) Go ahead and add # followed by some text then ## followed by some more text (hint: This will become a header).  

# This is a First Level heeader 

## This is a Second level header

Hit the "Render" button above.

2.) One the sentence below place this ** in front and after the words "bold text." Now do this again but to the words "italic text" but with only one star on each end.  

This is  **bold text**.  

This is *italic text*.  


Hit the "Render" button above.


3.) Head to the YAML at the top and enter your name author section. (Hint: be sure to remove the # in front of the word, you will also need " ")


Hit the "Render" button above.  


4.) Add the word "sketchy" to the end of theme in the YAML. (Hint: don't include the " "). 


Hit the "Render" button above.


5.) Copy and paste this [](https://quarto.org/docs/output-formats/html-themes.html) and enter the word "Click Here" in between the [ ] (hint: don't include the " ").


[Click Here](https://quarto.org/docs/output-formats/html-themes.html)




6.) Copy and paste the following equation e = mc^2 below, now put $ in front and after it. 


$e=mc^2$


7.) Head to the top right corner of your screen and click the +c button that is next to the ⬆️ arrow. 

```{r}



```


8.) Within the code chunk enter 1+1

```{r}

1+1 


```



**Bonus:** *(Only for 'Last of Us' fans 🙃)*


```{r}
#| warning: false
#| message: false

if (!require("devtools")) install.packages("devtools") # installs devtools if you don't have it

library(devtools)  

devtools::install_github("nvietto/nopunintended") 

library(nopunintended)

nopunintended()


```




